Study locations

### 2022-09-01 Scripts/Map_study_locations.Rmd
karise dataset
manicor dataset

---
title: "Untitled"
output: html_document
---

@@

#Rename list and 
names(data) <- file_names
data = bind_rows(data,  .id = 'Study_id')
data_coord <- st_as_sf(data, coords = c(3:4)) %>% 
st_set_crs(4326) %>% 
st_transform(3035)

>>>>

---
title: "Study locations"
output: html_document
---

@@

#Rename list and 
names(data) <- file_names
data = bind_rows(data,  .id = 'Study_id')

#Add manual jitter to these three points
data = data %>% 
mutate(Latitude = case_when(Study_id == "16_Manicor" ~ Latitude+0.25, TRUE ~ Latitude)) %>% mutate(Latitude = case_when(Study_id == "17_Manicor" ~ Latitude+0.25, TRUE ~ Latitude)) %>%
mutate(Latitude = case_when(Study_id == "18_Manicor" ~ Latitude+0.25, TRUE ~ Latitude))

data_coord <- st_as_sf(data, coords = c(3:4)) %>% 
st_set_crs(4326) %>% 
st_transform(3035)
